Comparing R packages for calculation of persistent homology

### 2020-01-26 tdabench-paper/tdabench.Rmd
Really struggling with the 150 word count

---
title: Comparing R packages for calculation of persistent homology
author:
  - name: Eashwar V. Somasundaram
    affiliation: School of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44106, United States
    email: eashwar.somasundaram@case.edu
  - name: Shael E. Brown
    affiliation: Department of Quantitative Life Sciences
    address:
    - McGill University
    - Montreal, QC H3A 0G4, Canada
    email: shael.brown@mail.mcgill.ca
  - name: Adam Litzler
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195, United States
    email:  adli4611@colorado.edu
  - name: Jacob G. Scott
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195, United States
    email: ScottJ10@ccf.org
  - name: Raoul R. Wadhwa
    affiliation: Cleveland Clinic Lerner College of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44195, United States
    email: raoul.wadhwa@case.edu
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

>>>>

---
title: Comparing R packages for calculation of persistent homology
author:
  - name: Eashwar V. Somasundaram
    affiliation: School of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44106, United States
    email: eashwar.somasundaram@case.edu
  - name: Shael E. Brown
    affiliation: Department of Quantitative Life Sciences
    address:
    - McGill University
    - Montreal, QC H3A 0G4, Canada
    email: shael.brown@mail.mcgill.ca
  - name: Adam Litzler
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195, United States
    email:  adli4611@colorado.edu
  - name: Jacob G. Scott
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195, United States
    email: ScottJ10@ccf.org
  - name: Raoul R. Wadhwa
    affiliation: Cleveland Clinic Lerner College of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44195, United States
    email: raoul.wadhwa@case.edu
abstract: >
  Several persistent homology software libraries have been implemented in R. The Dionysus (TDA), GUDHI (TDA), and Ripser C++ libraries (TDAstats) provide Rips complex functionality. GUDHI  (TDA package) also provides Alpha complex functionality. These software represent powerful analysis tools but are limited computationally. These limitations and guidelines for which persistent homology libraries to use have not been specified in R. We benchmarked the all libraries on a High-Powered Cluster for runtime. We also compared Alpha and Rips for memory burden. Alpha complexes run significantly faster than all Rips complex libraries for all data sets for data dimension less than or equal to three. Alpha complexes were not computable for data dimension greater than 3. TDAstats had the fastest runtimes for all Rips complexes. We recommend performing persistent homology with GUDHI Alpha complexes for data dimension less than or equal to three. For higher dimension, we recommend TDAstats Rips Complex. 
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---
